Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-06-11 Silvers_cfmip.tex
updated Silvers_cfmip.tex tex file
Silvers_cfmip.tex and Silvers_cfmip_extraTable.tex

@@

\begin{figure}
  \centering
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
  \caption{Observed and modeled clouds below 2.75km.  Clouds shown are divided into thick 
  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
  (AM4) are 18\% (13\%) for thick clouds and 22\% (6\%) for thin clouds}
  \label{fig:cf_misr_lowcl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_climo_hist_amip_obs_10yr.eps}
  \caption{Comparison of cloud fraction among observations from CALIPSO, the \textit{amip} and 
  \textit{historical} experiments.  To maximize the overlapping years with the observation period of CALIPSO
  (January 2007 - December 2016), only the 10 year period between January 2005 and December 2014 is
  used from the \textit{amip} and  \textit{historical} experiments.  The cloud fraction from the full \textit{amip}
  time period and from early periods of the historical experiment are very similar 
  (almost entirely less than 1\% difference).   Note that the regions poleward of
  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  
  Coupling the atmosphere to a dynamic ocean only leads to slight improvements in the CF bias.}
  \label{fig:calipso_amip_historical}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/radflux_toa_netcre_ceres4p1.eps}
  \caption{Top-of-the-atmosphere CRE from CERES-EBAF ed4.1 and from the AM4.0 \textit{amip} experiment.  
  The bottom row shows the AM4.0 bias (CERES-AM4.0) for the LW CRE and SW CRE components.}
  \label{fig:ceres_cre_4p1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_base_amips_calip.eps}
  \caption{Vertical and latitudinal structure of cloud fraction for \textit{amip}-related experiments and observations from 
  CALIPSO.  The \textit{amip}-related experiments include a uniform warming of 4K (\textit{amip-p4K}), 
  a uniform cooling of 4K (\textit{amip-m4K}), and a 
  patterned warming with a global mean of 4K (\textit{amip-future4K}).  See text for details.}
  \label{fig:calipso_amip_comparison}
\end{figure}

@@

>>>>

It has been claimed that cloud feedbacks in simplified experiments match those in full models (Ringer et al., 2014, Medeiros et al?).  
Does this work support such a claim?

@@

\begin{figure}
  \centering
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cf_misr_cldfrac_below3km.eps}
  \caption{Observed and modeled clouds below 2.75km.  Clouds shown are divided into thick 
  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
  (AM4) are 18\% (13\%) for thick clouds and 22\% (6\%) for thin clouds}
  \label{fig:cf_misr_lowcl}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cloudfrac_climo_hist_amip_obs_10yr.eps}
  \caption{Comparison of cloud fraction among observations from CALIPSO, the \textit{amip} and 
  \textit{historical} experiments.  To maximize the overlapping years with the observation period of CALIPSO
  (January 2007 - December 2016), only the 10 year period between January 2005 and December 2014 is
  used from the \textit{amip} and  \textit{historical} experiments.  The cloud fraction from the full \textit{amip}
  time period and from early periods of the historical experiment are very similar 
  (almost entirely less than 1\% difference).   Note that the regions poleward of
  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  
  Coupling the atmosphere to a dynamic ocean only leads to slight improvements in the CF bias.}
  \label{fig:calipso_amip_historical}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/radflux_toa_netcre_ceres4p1.eps}
  \caption{Top-of-the-atmosphere CRE from CERES-EBAF ed4.1 and from the AM4.0 \textit{amip} experiment.  
  The bottom row shows the AM4.0 bias (CERES-AM4.0) for the LW CRE and SW CRE components.}
  \label{fig:ceres_cre_4p1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cloudfrac_base_amips_calip.eps}
  \caption{Vertical and latitudinal structure of cloud fraction for \textit{amip}-related experiments and observations from 
  CALIPSO.  The \textit{amip}-related experiments include a uniform warming of 4K (\textit{amip-p4K}), 
  a uniform cooling of 4K (\textit{amip-m4K}), and a 
  patterned warming with a global mean of 4K (\textit{amip-future4K}).  See text for details.}
  \label{fig:calipso_amip_comparison}
\end{figure}

@@

% ceres data is here on my macbook: 
% /Users/silvers/data/SatData/CERES/CERES_EBAF-TOA_Ed2.8_Subset_200003-201607.nc
% /Users/silvers/data/SatData/CERES/CERES_EBAF_Ed4.1_Subset_200003-201809.nc

% how exactly should I cite the CERES data?  Looking here: https://eosweb.larc.nasa.gov/project/ceres/ebaf_ed4.1. I don't see a 
% particular paper to cite, just DOI's.  The info from ncdump implies that the data extends along 200003-201809, which is confirmed by
% 223 time steps that are presumably monthly....  but in the global attributes section of the output from ncdump it states: 
%:title = "CERES EBAF TOA and Surface Fluxes. Monthly Averages and 07/2005 to 06/2015 Climatology." ;
%                :institution = "NASA Langley Research Center" ;
%                :Conventions = "CF-1.4" ;
%                :comment = "Climatology from 07/2005 to 06/2015" ;
%                :version = "Edition 4.1; Release Date May 28, 2019" ;
%                :DOI = "10.5067/TERRA-AQUA/CERES/EBAF_L3B004.1"

% what does the comment about climatology mean?

### 2020-06-11 Silvers_cfmip_extraTable.tex
Silvers_cfmip.tex and Silvers_cfmip_extraTable.tex

We calculate feedbacks for the coupled experiments, and amip, as follows.     The difference in surface temperature is calculated 
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.   
The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
to years 1996-2015.

@@

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years... }
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
 Feedback   & Abrupt 4xCO2 & 1pct.   & Historical    &  Amip   \\ \hline
    Net          &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
    \\
    Net CRE   & -0.06       &  -0.26          & -0.45         & -0.46           \\  
    \\
    LW CRE   & 0.14        &  0.10            & -0.14           & -0.03          \\  
    \\
    SW CRE  & -0.20       &  -0.26            & -0.31          & -0.43         \\  
    \\
    LW CLR   & -1.70       &  -1.71            & -1.94           & -2.25        \\  
    \\
    SW CLR  & 0.65        & 0.65              & 0.56             & 0.91          \\  
    \\
    $\Delta \rm{T}_s$        & 3.99        &  ??                & 0.8              & 0.76          \\  \hline

>>>>

We calculate feedbacks for the coupled experiments, and amip, as follows.     The difference in surface temperature is calculated 
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.   
The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
to years 1996-2015 (Is it correct that $T_2$ and $N_2$ correspond to different years?).

@@

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux.}
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
 Feedback   & Abrupt 4x$\rm{CO}_2$ & 1pct$CO_2$.   & Historical    &  Amip   \\ \hline
    Net $\alpha$         &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
    \\
    Net CRE   & -0.06       &  -0.26          & -0.45         & -0.46           \\  
    \\
    LW CRE   & 0.14        &  0.10            & -0.14           & -0.03          \\  
    \\
    SW CRE  & -0.20       &  -0.26            & -0.31          & -0.43         \\  
    \\
    LW CLR   & -1.70       &  -1.71            & -1.94           & -2.25        \\  
    \\
    SW CLR  & 0.65        & 0.65              & 0.56             & 0.91          \\  
    \\
    $\Delta \rm{T}_s$        & 3.99        &  ??                & 0.8              & 0.76          \\  \hline
